\documentclass[12pt]{article}
%\usepackage[vmargin=1.5cm, hmargin=1.5cm]{geometry}                
%\geometry{letterpaper}           
\usepackage[letterpaper, margin=1.87cm]{geometry}
%\usepackage{times}
\usepackage{graphicx, hanging, mdwlist, titlesec}
\usepackage{amssymb, fancyhdr, enumitem}
\usepackage{threeparttable, subfigure, multirow}
\usepackage{hyperref}
\usepackage{tikz}

%Header
\renewcommand{\headrulewidth}{0pt} 
\fancyhf{}
\lhead{\textbf{Matthew M Osmond} \textit{Curriculum Vitae}}
\rhead{\thepage}

\setitemize{noitemsep, topsep=1pt} %space bw items and bw paras and items in itemize enviro
\titlespacing{\subsection}{0pt}{*1}{*0}

\newcommand*{\ClipSep}{0.4cm}%

\begin{document}
\thispagestyle{empty} 
\pagestyle{fancy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{center}
{\raggedleft
\noindent\Large{\textbf{MATTHEW M.\ OSMOND}}\\
\large Assistant Professor\\
\large Ecology \& Evolutionary Biology\\
\large University of Toronto \\
\large mm.osmond@utoronto.ca\\
\href{https:/osmond-lab.github.io}{osmond-lab.github.io}\\
%\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabular}{lll}
\textbf{Prof.} & Department of Ecology \& Evolutionary Biology, University of Toronto\hspace{0.5cm} & 2021-\\
\\
\textbf{PDF} & Center for Population Biology \& Banting Fellow, UC Davis & 2018-2020\\
& Mentors: Graham Coop, Sebastian Schreiber, Andrew Whitehead\\
\\
%\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section*{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{tabular}{lll}
\textbf{PhD} & Zoology, University of British Columbia & 2013 - 2018\\
& Title: \textit{Adaptive challenges: fitness valleys and evolutionary rescue}\\
& Supervisor: Sarah Otto\\
& Committee: Amy Angert, Michael Doebeli, Michael Whitlock\\
\\
\textbf{MSc} & Biology, McGill University & 2010 - 2012 \\
& Title: \textit{Eco-evolutionary rescue: an adaptive dynamic analysis}  \\
& Supervisor: Claire de Mazancourt\\
& Committee: Michel Loreau, Fr\'{e}d\'{e}ric Guichard\\
\\
\textbf{BSc} &  Mathematics \& Biology, Queen's University & 2004 - 2008\\ %(83\% Avg.)
& Honours title: \textit{The meaning of female coloration in the American redstart}  \\
& Supervisors: Laurene Ratcliffe, Matt Reudink\\
& Committee: Paul Martin\\
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Selected Awards and Grants}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabular}{llr}
  2021-2026 & Discovery Grant, NSERC & \$202,500 \\
%  2020 & Young Investigator (Travel) Award, Society for Molecular Biology and Evolution & \\
  2019-2020 & Banting Postdoctoral Fellowship, Canada & \$140,000 \\
  2018-2020 & Center for Population Biology Postdoctoral Fellowship, UC Davis & \$125,000 \\
  2018-2020 & Postdoctoral Fellowship, NSERC (awarded but declined) & \$90,000 \\
%  2018 & Talk award, Evo-WIBO & a book\\ 
%  2017-2018 & Graduate Student Fellowship, University of British Columbia & \$16,500 \\
%  2017 & Zoology Graduate Student Travel Award, University of British Columbia \\%& \$500\\ 
%  2015 & Zoology Graduate Student Travel Award, University of British Columbia \\%& \$500\\ 
%  2015 & $2^{nd}$ best talk, Canadian Society for Ecology and Evolution Meeting & \$300\\ 
%  2013 & BRITE Travel Award, University of British Columbia \& NSERC \\%& \$500\\
%  2013 & International Research Mobility Award, University of British Columbia \\%& \$1,500\\ 
  2013-2017 & Alexander Graham Bell Canada Graduate Scholarship, NSERC & \$105,000\\
%  2013-2014 & Faculty of Science Graduate Award, University of British Columbia & \$6,000\\
%  2013-2018 & Four Year Fellowship, University of British Columbia & \$18,000\\
%  2013-2014 & BRITE Fellowship, University of British Columbia \& NSERC & \$6,000\\
  2011-2012 & Alexander Graham Bell Canada Graduate Scholarship, NSERC & \$17,500\\
  2011-2012 & Dr.\ Neal Simon Memorial Scholarship & \$1,000\\
%  2011-2012 & Excellence Award, Quebec Centre for Biodiversity Science & \$2,500\\
%  2011 & Graduate Research Enhancement and Travel Award, McGill University \\%& \$500\\
%  2010 & Provost's Graduate Fellowship, McGill University \\%& \$1,500\\
%  2010-2011 & Science and Technology Award, Ontario Graduate Scholarship & \$5,000\\
%  2009 & Faculty Research Scholarship, Lakehead University \\%& \$4,666\\
%  2008 & B.Sc.\ Honours with Distinction, Queen's University \\%& \$0 \\
%  2008 & Undergraduate Student Research Award (USRA), NSERC (declined) & \$4,500\\
  2007 & Undergraduate Student Research Award, NSERC & \$4,500\\
%  2005 & Annie Bentley Lillie Prize, First Year Calculus, Queen's University \\%& \$0\\
  %2004 - 2008 & Dean's Honour List, Queen's University\\
\end{tabular}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hangpara{1cm}{1}\noindent\hspace{.1cm}\textcolor{gray}{16. \textbf{Osmond M}, Coop G. (Submitted). Estimating dispersal rates and locating genetic ancestors with genome-wide genealogies. \textit{bioR$\chi$iv} 10.1101/2021.07.13.452277.}

\hangpara{1cm}{1}\noindent\hspace{.1cm}15. Lyberger K, \textbf{Osmond M}, Schreiber S. 2021. Is evolution in response to extreme events good for population persistence? \textit{The American Naturalist} 198:44-52.

\hangpara{1cm}{1}\noindent\hspace{.1cm}14. Klausmeier C, \textbf{Osmond M}, Kremer C, Litchman E. 2020. Ecological limits to evolutionary rescue. \textit{Philosophical Transactions of the Royal Society B}. 375:20190453

\hangpara{1cm}{1}\noindent\hspace{.1cm}13. Henriques GJB, \textbf{Osmond M}. 2020. During environmental change, cooperation can promote rescue or lead to evolutionary suicide. \textit{Evolution} 74:1255-1273.

\hangpara{1cm}{1}\noindent\hspace{.1cm}12. \textbf{Osmond M}, Coop G. 2020. Genetic signatures of evolutionary rescue by a selective sweep. \textit{Genetics} 215:813-829.

\hangpara{1cm}{1}\noindent\hspace{.1cm}11. \textbf{Osmond M}, Otto SP, Martin G. 2020. Genetic paths to evolutionary rescue and the distribution of fitness effects along them. \textit{Genetics} 214:493-510.

\hangpara{1cm}{1}\noindent\hspace{.1cm}10. Thompson K, \textbf{Osmond M}, Schluter D. 2019. Parallel genetic evolution and speciation from standing variation. \textit{Evolution Letters} 3:129-141.

\hangpara{1cm}{1}\noindent\hspace{.1cm}9. Edwards K, Kremer C, Miller E, \textbf{Osmond M}, Litchman E, Klausmeier C. 2018. Evolutionary stable communities: a framework for understanding the role of trait evolution in the maintenance of diversity. \textit{Ecology Letters} 21:1853-1868.

\hangpara{1cm}{1}\noindent\hspace{.1cm}8. Scott M$^*$, \textbf{Osmond M}$^*$, Otto S. 2018. Haploid selection, sex ratio bias, and transitions between sex-determining systems. \textit{PLoS Biology} 16:e2005609. [$^*$ joint first authors]

\hangpara{1cm}{1}\noindent\hspace{.1cm}7. \textbf{Osmond M}, Klausmeier C. 2017. An evolutionary tipping point in a changing environment. \textit{Evolution} 71:2930-2941.

\hangpara{1cm}{1}\noindent\hspace{.1cm}6. \textbf{Osmond M}, Otto S, Klausmeier C. 2017. When predators help prey adapt and persist in a changing environment. \textit{The American Naturalist} 190:83-98. [F1000Prime Recommended]

\hangpara{1cm}{1}\noindent\hspace{.1cm}5. \textbf{Osmond M}, Barbour M, Bernhardt J, Pennell M, Sunday J, O'Connor M. 2017. Warming induced changes to body size stabilize consumer-resource dynamics. \textit{The American Naturalist} 189:718-725.

\hangpara{1cm}{1}\noindent\hspace{.1cm}4. Toews D, Delmore K, \textbf{Osmond M}, Taylor P, Irwin D. 2017. Migratory orientation in a narrow avian hybrid zone. \textit{PeerJ} 5:e3201.

\hangpara{1cm}{1}\noindent\hspace{.1cm}3. \textbf{Osmond M}, Otto S. 2015. Fitness-valley crossing with generalized parent-offspring transmission. \textit{Theoretical Population Biology} 105:1-16. %dx.doi.org/10.1016/j.tpb.2015.08.002.

\hangpara{1cm}{1}\noindent\hspace{.1cm}2. \textbf{Osmond M}, Reudink M, Marra P, Germain R, Nocera J,  Boag P, Ratcliffe L.  2013. Relationships between carotenoid-based female plumage and age, reproduction, and mate colour in the American Redstart. \textit{Canadian Journal of Zoology} 91:589-595. %dx.doi.org/10.1139/cjz-2013-0017.

\hangpara{1cm}{1}\noindent\hspace{.1cm}1. \textbf{Osmond M}, de Mazancourt C. 2013. How competition affects evolutionary rescue. \textit{Philosophical Transactions of the Royal Society B: Biological Sciences} 368:20120085. %dx.doi.org/10.1098/rstb.2012.0085.

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Invited Seminars}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hangpara{0.5cm}{1}Osmond M, Coop G. 2021. Estimating dispersal rates and locating genetic ancestors with genome-wide genealogies. Biological Sciences Weekly Seminar Series, \textbf{Northern Arizona University}, Flagstaff, USA. (virtual)

\hangpara{0.5cm}{1}Osmond M, Coop G. 2020. \texttt{spaARG}: Inferring dispersal rates and the locations of genetic ancestors from genome-wide gene genealogies. Computational and Theoretical Evolutionary Genetics seminar series, \textbf{University of California - Berkeley}, Berkeley, USA. (virtual)

\hangpara{0.5cm}{1}Osmond M. 2020. Evolutionary rescue: genetic basis and genetic signatures. Rescue Team online seminar series, \textbf{Max Planck Institute for Evolutionary Biology}, Pl\"{o}n, Germany. (virtual)

\hangpara{0.5cm}{1}Osmond M. 2018. Evolutionary rescue: adaptation, genetics, demography. \textbf{University of Toronto}, Toronto, Canada.

\hangpara{0.5cm}{1}Osmond M, Martin G, Ronce O, Otto S. 2018. Evolutionary rescue. Mathematical Biology Seminar, \textbf{University of British Columbia}, Vancouver, Canada.

\hangpara{0.5cm}{1}Osmond M. 2018. Evolutionary rescue: integrating ecological and evolutionary theory. Center for Population Biology, \textbf{University of California - Davis}, Davis, USA. 

\hangpara{0.5cm}{1}Osmond M, Martin G, Otto S, Ronce O. 2016. Genetic signatures of evolutionary rescue with sex. Stochastic Models for the Inference of Life Evolution group, \textbf{College de France}, Paris, France. 

\hangpara{0.5cm}{1}Osmond M, Otto S, Klausmeier C. 2016. When predators help prey adapt and persist. \textbf{Institute National de la Recherche Agronomique}, Montpellier, France. 

\hangpara{0.5cm}{1}Osmond M, Otto S. 2016. Subcritical adaptation: fitness valleys and evolutionary rescue. Stochastic and Deterministic Models for Evolutionary Biology workshop, \textbf{Oaxaca}, Mexico. 

%\hangpara{0.5cm}{1}\textbf{Osmond, M.}* and Otto, S.P., 2014. Crossing fitness-valleys without the help of Mendel. Talk, Biomathematics Group, University of Helsinki.

\hangpara{0.5cm}{1}Osmond M, de Mazancourt C. 2013. Using adaptive dynamics to predict evolution and extinction in changing environments. Pacific Institute for the Mathematical Sciences, \textbf{University of British Columbia}, Vancouver, Canada.

%\hangpara{0.5cm}{1}\textbf{Osmond M}*, de Mazancourt C. 2012. Using adaptive dynamics to predict evolution and extinction in changing environments. Talk, Biomathematics Group, University of Helsinki, Finland.

\hangpara{0.5cm}{1}Osmond M, de Mazancourt C. 2011. To adapt and persist in a changing environment. Mick Follows lab, \textbf{Massachusetts Institute of Technology}, Boston, USA.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Service}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{Associate Editor} \textit{Theoretical Population Biology} (2021-)\\
\noindent \textbf{Reviewer} \textit{The American Naturalist} (12), \textit{Evolution} (3), \textit{Genetics} (3), \textit{Ecology Letters} (2), \textit{Evolution Letters} (2), \textit{Journal of Theoretical Biology} (2), \textit{Theoretical Population Biology} (3), \textit{Biological Journal of the Lineann Society} (1), \textit{Ecology} (1), \textit{Ecology and Evolution} (1), \textit{eLife} (1), \textit{Frontiers in Ecology and Evolution} (1), \textit{Global Change Biology} (1), \textit{Heredity} (1), \textit{Molecular Biology and Evolution} (1), \textit{Molecular Ecology} (1), \textit{Nature Communications} (1), \textit{Nature Ecology and Evolution} (1), \textit{Philosophical Transactions of the Royal Society B} (1), \textit{Journal of Statistical Mechanics} (1), \textit{PLoS Computational Biology} (0.5), \textit{Science} (0.5)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Membership}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Society for Molecular Biology \& Evolution, 2020-\\
\noindent Society for the Study of Evolution, 2019- \\
\noindent Genetics Society of America, 2018- \\
\noindent American Society of Naturalists, 2014- \\
\noindent Canadian Society for Ecology and Evolution, 2011-

\end{document}